---
title: "Plotly Assignment"
subtitle: "<span style='font-size:22px;'>Please click on the right border of the slide to view the next one.</span>"
output: ioslides_presentation
author: lavender-cherimoya
date: "2024-08-26"
---

## R Code
The following code uses the ChickWeight database, which contains the weight data in gram of 48 individual chicks during their growth, as a function of time and diet. There are 4 different diets, and the timeframe goes from 0 to 21 days maximum. 

```{r slide1, echo=FALSE, error=FALSE, warning=FALSE, message=FALSE}
library(plotly)
library(dplyr)
```

```{r slide1_2, echo=TRUE, error=FALSE, warning=FALSE, message=FALSE}

plots <- ChickWeight %>%
  split(.$Diet) %>%
  lapply(function(df) {
    plot_ly(df, x = ~Time, y = ~weight, color = ~Chick, 
            colors = "Set2", type = 'scatter', 
            mode = 'lines+markers', marker = list(size = 5)) %>%
      layout(xaxis = list(title = "Time [days]"),
             yaxis = list(title = "Weight [g]"),
             showlegend = FALSE)
  })
```

## Chick growth trajectories

The plot below shows individual chick weight growth grouped by diet, with each subplot representing a different diet and each curve a different chick.

```{r slide2, echo=FALSE, error=FALSE, warning=FALSE, message=FALSE}
plotly_plot <- subplot(plots, nrows = 2, shareX = TRUE, shareY = TRUE, titleY = TRUE)%>%
  layout(title = "Chick growth as a function of diet and time",
         annotations = list(
           list(x = 0.225, y = 1.0, text = "Diet 1", showarrow = FALSE, xref='paper', yref='paper'),
           list(x = 0.775, y = 1.0, text = "Diet 2", showarrow = FALSE, xref='paper', yref='paper'),
           list(x = 0.225, y = 0.45, text = "Diet 3", showarrow = FALSE, xref='paper', yref='paper'),
           list(x = 0.775, y = 0.45, text = "Diet 4", showarrow = FALSE, xref='paper', yref='paper')
         ))

plotly_plot
```

